|

### 2023-06-08 manuscript/paper.Rmd
adding refs

Ecological release theory suggests that a prey population’s niche should shift and expand when predation is relaxed or removed (reviewed in @Herrmann2021). 
Niche expansion could manifest through a combination of increasing within- and between-individual niche widths (@Bolnick2010; @Herrmann2021), including divergence between the sexes (@Bolnick2003; @Cooper2011). Theory and empirical data suggest that a population presented with novel ecological opportunity might experience disruptive selection on males and females stemming from intraspecific competition over newly accessible resources, resulting in intersexual divergence in habitat use (Schoener 1968; @Shine1989; @Bolnick2003; @Butler2007; @Bolnick2008; @Cooper2011; but see @Stuart2021; @Blain2022). Accordingly, sexes should also diverge in morphological phenotypes associated with habitat use; such ecologically-driven "character displacement between the sexes" is therefore one explanation for sexual dimorphism (de Lisle papers).

>>>>

Ecological release theory suggests that a prey population’s niche should shift and expand when predation is relaxed or removed (reviewed in @Herrmann2021). 
Niche expansion could manifest through a combination of increasing within- and between-individual niche widths (@Bolnick2010; @Herrmann2021), including divergence between the sexes (@Bolnick2003; @Cooper2011). Theory and empirical data suggest that a population presented with ecological opportunity following ecological release might experience disruptive selection on males and females stemming from intraspecific competition over newly accessible resources, resulting in intersexual divergence in habitat use (@Schoener1968; @Shine1989; @Bolnick2003; @Butler2007; @Bolnick2008; @Cooper2011; but see @Stuart2021; @Blain2022). Accordingly, sexes should also diverge in morphological traits associated with habitat use; such ecologically-driven "character displacement between the sexes" is therefore one explanation for sexual dimorphism (@deLisleRowe2015; @deLisleNco2018).
